---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# islay

<!-- badges: start -->
<!-- badges: end -->

The goal of the islay package is to provide a high-quality teaching dataset for archaeologists using R.
It includes various datasets relating to the prehistoric archaeology of the Scottish island of Islay (pronounced "EYE-luh") and recorded by the 'Southern Hebrides Mesolithic Project' (Mithen et al. 2000).

```{r readme-figure, echo=FALSE}
library(islay)
library(ggplot2)
suppressMessages(library(sf))

periods <- c("Mesolithic", "Mesolithic & Later Prehistoric", "Later Prehistoric")

ggplot(islay_sites) +
  geom_sf(data = islay_land) +
  geom_point(aes(longitude, latitude, colour = factor(period, periods))) +
  scale_colour_brewer(palette = "Set1", 
                      guide = guide_legend(title = NULL)) +
  coord_sf(crs = 27700, default_crs = 4326, label_graticule = "") +
  labs(x = NULL, y = NULL) +
  theme_minimal() +
  theme(
    legend.position = c(0, 0),
    legend.justification = c(0, 0)
  )
```

## Installation

You can install the development version of islay from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("joeroe/islay")
```

## Example

The package currently includes one dataset, `islay_sites`:

```{r eg-islay-sites}
library(islay)
islay_sites
```
